Lens Modeling in \sw

### 2013-09-09 text/tex/spaghetti.tex
still editing

It provides a web based graphical user interface that allows to trace contours with the mouse and identify extremal points by clicking on the image.

@@

The modelling process consitis of three basic steps:
\begin{enumerate}
  \item identify lensed images and separate them from other background light sources
  \item classify and order images accoring to arrival time. (local minima, maxima, saddlepoints)
  \item fine tune the arrangement, identify addidional external point masses influencing the result
\end{enumerate}

\spl assists volunteers with several features in this process.
Step 1 by supplying several images from several bands (not yet implemented in \sw).
Step 2 by restricting the user, only valid configuration can be entered, the odd number theorem\needcite is taken care of.

>>>>

The exact placement of the pink spaghetti loops shown in
Figure~\ref{fig:input-spag} has no significance.  Their utility is
just to help mark up the image as maximum, minima and saddle points.
As the figure suggests, the marking up can be done very easily with a
mouse.  Human intuition is required to (a)~identify lensed images and
separate them from other background light sources, and (b)~classify
and order images accoring to arrival time.  But the computer helps by
allowing only valid lensing configurations to be entered, and ensuring
that the odd image theorem\needcite is taken care of.

@@

\spl assists volunteers with several features in this process.
Step 1 by supplying several images from several bands (not yet implemented in \sw).
